Labor Market Income and Substitution Effects Explain Contemporary Natural Selection

### 2020-12-18 why-natural-selection.Rmd
Tweaks

[^purifying]: We also check for purifying selection by estimating (\@ref(eq:regression)) with a quadratic term in $PGS_i$. See Appendix figure \@ref(fig:plot-purifying).

@@

We rerun equation (\@ref(eq:regression)), adding a quadratic term in $PGS_i$,
and using our age/qualification weights. Scores for hip circumference and drinks
per week show significant purifying selection ($p < 0.05/33$, negative
coefficient). Scores for educational attainment (EA2 and EA3) show significant
diversifying selection ($p < 0.05/33$, positive coefficient), which reduces the
strength of selection against educational attainment at very high levels of the 
PGS. Figure
\@ref(fig:plot-purifying) plots predicted number of children against polygenic
score from these regressions.

>>>>

[^purifying]: We also check for purifying selection by estimating \@ref(eq:regression) with a quadratic term. See Appendix Figure \@ref(fig:plot-purifying).

@@

We rerun equation \@ref(eq:regression), adding a quadratic term in $PGS_i$,
and using our age/qualification weights. Scores for hip circumference and drinks
per week show significant purifying selection ($p < 0.05/33$, negative
coefficient). Scores for educational attainment (EA2 and EA3) show significant
diversifying selection ($p < 0.05/33$, positive coefficient), which reduces the
strength of selection against educational attainment at very high levels of the 
PGS. Figure
\@ref(fig:plot-purifying) plots predicted number of children against polygenic
score from these regressions.
